Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 21:11

Following the application of the above discussed methodology to the entire dataset 
(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The stronger CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation .

@@

Another interesting aspect of the CE events, is their distribution within the year. In
Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the monthly box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months, the occurrences gradually ramp between the maximum and minimum.
This seasonality is a combinations of the clouds occurrences, and the relevant
position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
formation, type and location is not allowing further analysis.

>>>>

Following the application of the above discussed methodology to the entire dataset 
(`r round(ST_total$wattGLB.N / 10^6,1)` million of one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The stronger CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation.

@@

!!! monthly weithe !!!

Another interesting aspect of the CE events is their distribution within the year.
Figure\nobreakspace{}\ref{fig:relative-month-occurrences} shows the monthly box 
and whisker plot of the CE number of occurrence normalized with the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months, the occurrences gradually ramp between the maximum and minimum.
This seasonality is a combinations of the clouds occurrences, and the relevant
position of the sun during each season of the year. Unfortunately, the lack of detailed data on cloud
formation, type and location is not allowing further analysis.

### 2024-06-11 article/article.tex
Commit 2024-06-11 21:11

Following the application of the above discussed methodology to the
entire dataset (6.1 million of one-minute GHI measurements),
\(1.764\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
events. The highest recorded GHI due to CE was
\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OIR of
\(345.9\,\text{W}/\text{m}^2\). The stronger CE event of \(49.7\,\%\)
above the clear sky threshold was observed on 28~October 2016. In the
following sections we are discussing the long-term trends and
variability of the CE events as well as of the corresponding OIR and
excess irradiation .

@@

Another interesting aspect of the CE events, is their distribution
within the year. In
Figure\nobreakspace{}\ref{fig:relative-month-occurrences}, we have the
monthly box plot (whisker plot), where the values have been normalized
by the highest median value, that occurs on June. Although the number of
occurrences has a wide spread throughout the study period, the most
active period of CE occurrences is during May and June. During the
Winter (December -- February) the CE cases are about \(25\,\%\) of the
maximum. For the rest months, the occurrences gradually ramp between the
maximum and minimum. This seasonality is a combinations of the clouds
occurrences, and the relevant position of the sun during each season of
the year. Unfortunately, the lack of detailed data on cloud formation,
type and location is not allowing further analysis.

>>>>

Following the application of the above discussed methodology to the
entire dataset (6.1 million of one-minute GHI measurements),
\(1.764\,\%\) were identified as CE events and \(0.036\,\%\) as ECE
events. The highest recorded GHI due to CE was
\(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, corresponding to OIR of
\(345.9\,\text{W}/\text{m}^2\). The stronger CE event of \(49.7\,\%\)
above the clear sky threshold was observed on 28~October 2016. In the
following sections we are discussing the long-term trends and
variability of the CE events as well as of the corresponding OIR and
excess irradiation.

@@

!!! monthly weithe !!!

Another interesting aspect of the CE events is their distribution within
the year. Figure\nobreakspace{}\ref{fig:relative-month-occurrences}
shows the monthly box and whisker plot of the CE number of occurrence
normalized with the highest median value, that occurs on June. Although
the number of occurrences has a wide spread throughout the study period,
the most active period of CE occurrences is during May and June. During
the Winter (December -- February) the CE cases are about \(25\,\%\) of
the maximum. For the rest months, the occurrences gradually ramp between
the maximum and minimum. This seasonality is a combinations of the
clouds occurrences, and the relevant position of the sun during each
season of the year. Unfortunately, the lack of detailed data on cloud
formation, type and location is not allowing further analysis.
